From noise to knowledge: how randomness generates novel phenomena and reveals information

### 2017-11-01 paper/paper.Rmd
fix citation

keywords:
  - stochasticity
  - demographic noise
  - environmental noise
  - colored noise
  - quasi-cycles

@@

Most importantly, the framing of stochastic processes as indicators of 
changes in an ecosystem that might otherwise go unnoticed has proven a
rich catalyst for bringing these concepts beyond the realm of abstract
theory. A rich array of experimental and observational tests of early
warning signals [_i.e._ @Carpenter2011; @Dai2012; and many others, _e.g._ see @Scheffer2015 review] has served no merely to illustrate these phenomena can be seen
in laboratory and field ecosystems, but also to spark suggestions of
additional possible indicators and surface a wide array of 
practical [@Boettiger2013b; @Scheffer2015], statistical [e.g. @Boettiger2012d; @Boettiger2012], and theoretical [e.g. @Dai2015; @Wysham2010] challenges to such application.  This
creates a two-way dialog between empirical and theoretical work that does
much to advance the field as a whole.

>>>>

keywords:
  - stochasticity
  - demographic noise
  - environmental noise
  - colored noise
  - quasi-cycles
  - tipping points

@@

Most importantly, the framing of stochastic processes as indicators of 
changes in an ecosystem that might otherwise go unnoticed has proven a
rich catalyst for bringing these concepts beyond the realm of abstract
theory. A rich array of experimental and observational tests of early
warning signals [_i.e._ @Carpenter2011; @Dai2012; and many others, _e.g._ see @Scheffer2015 review] has served no merely to illustrate these phenomena can be seen
in laboratory and field ecosystems, but also to spark suggestions of
additional possible indicators and surface a wide array of 
practical [@Boettiger2013b; @Scheffer2015], statistical [e.g. @Boettiger2012d; @Boettiger2012], and theoretical [e.g. @Dai2015; @Hastings2010] challenges to such application.  This
creates a two-way dialog between empirical and theoretical work that does
much to advance the field as a whole.
